False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-08-31 ms.tex
conclusion work

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI).  Out of \ncalc\ KOIs, we determine
that \nval\ have probabilities $<$1\% to be astrophysical false
positives, and thus may be considered validated planets.  \nvalnew\ of
these have not yet been validated or confirmed by other methods.  In
addition, we identify \nfpnew\ KOIs likely to be false positives
($>$90\%) that have not yet been identified as such. A side
product of these calculations is full stellar property posterior
samplings for every host star, modeled as single, binary, and triple
systems.  These calculations use \vespa, a publicly available Python
package able to be easily applied to any transiting exoplanet
candidate.
\end{abstract}

@@

One final note about these FPP calculations is that unidentified
transit timing variations (TTVs) will increase the FPP of a transit
signal, as the shape of the folded light curve will be distorted,
typically resulting in a longer signal which a trapezoid model will
also identify as more V-shaped.  While we have analyzed light curves
using known TTVs when available, we have also undoubtedly missed many
systems with as-yet-unspecified TTV signals.  This means that a large
FPP may be simply an indication of unidentified TTVs rather than
indicative of an astrophysical false positive, especially in
multi-planet systems, which should overall have a very low false
positive rate.  \Tab{fpp} lists whether known TTVs were accounted for
when constructing the folded transit light curve for each KOI.

@@

In this work, we have calculated the astrophysical false positive
probability (FPP) for every \kepler\ object of interest (KOI), using
the publicly available Python module \vespa.  While the assumptions
behind this calculation are not necessarily valid for every KOI (see
\sect{results:fpp}), we have identified \nvalnew\ KOIs that have
reliable FPPs of $< 0.01$, resulting in validation of their planetary
nature at the 99\% confidence level, more than doubling the
number of confirmed \kepler\ exoplanets.

@@

While previous \emph{a priori} false positive rate estimates
\cite{Morton:2011b,Fressin:2013} have made clear that the
\kepler\ planet candidate catalogs are \emph{generally} low enough to
ignore for the purposes of planet occurrence rate calculations, any
more detailed study of any small subset of individual KOIs must
understand in more detail the FPPs of those specific candidates.  This
type of small-sample candidate culling using individually calculated
FPPs has already been done in the literature
\cite{MortonSwift:2014,MortonWinn:2015}; the publication of this full
catalog allows the community to do the same.

The \kepler\ mission has demonstrated that space-based transiting
planet surveys can identify viable planet candidates at a rate much
faster than traditional follow-up techniques can confirm them.  As a
result, probabilistic validation techniques are now

@@

%\capstartfalse
\input{table_fpp}
%\capstarttrue

>>>>

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI)---the first large-scale
demonstration of a fully automated transiting planet validation
procedure.  Out of \ncalc\ KOIs, we determine that \nval\ have
probabilities $<$1\% to be astrophysical false positives, and thus may
be considered validated planets.  \nvalnew\ of these have not yet been
validated or confirmed by other methods.  In addition, we identify
\nfpnew\ KOIs likely to be false positives that have not yet been
identified as such, though some of these may be a result of
unidentified transit timing variations. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple systems.  These
calculations use \vespa, a publicly available Python package able to
be easily applied to any transiting exoplanet candidate.
\end{abstract}

@@

One final note about these calculations is that unidentified
transit timing variations (TTVs) will increase the FPP of a transit
signal, as the shape of the folded light curve will be distorted,
typically resulting in a longer signal which a trapezoid model will
also identify as more V-shaped.  While we have analyzed light curves
using known TTVs when available, we have also undoubtedly missed many
systems with as-yet-unspecified TTV signals.  This means that a large
FPP may be simply an indication of unidentified TTVs rather than
indicative of an astrophysical false positive, especially in
multi-planet systems, which should overall have a very low false
positive rate.  \Tab{fpp} lists whether known TTV were accounted for
when constructing the folded transit light curve for each KOI.

@@

In this work, we have calculated the astrophysical false positive
probability (FPP) for every \kepler\ object of interest (KOI), using
the publicly available Python module \vespa.  While the assumptions
behind this calculation are not necessarily valid for every KOI (see
\sect{results:fpp}), we have identified \nvalnew\ KOIs that have
reliable FPPs of $< 0.01$, resulting in validation of their planetary
nature at the 99\% confidence level, more than doubling the number of
confirmed \kepler\ exoplanets.  Among this set of reliable \vespa\
calculations are also \nfpnew\ new likely false positive KOIs,
although we note that there is a chance that some of these large FPPs
are due to unidentified or miscorrected transit timing variations.

@@

While previous \emph{a priori} false positive rate estimates
\cite{Morton:2011b,Fressin:2013} have made clear that the
\kepler\ planet candidate catalogs are \emph{generally} low enough to
ignore for the purposes of planet occurrence rate calculations, any
more detailed study of any small subset of individual KOIs must
understand in more detail the FPPs of those specific candidates.  This
type of small-sample candidate culling using individually calculated
FPPs has already been done in the literature
\citep{MortonSwift:2014,MortonWinn:2015}; the publication of this full
catalog allows the community to do the same.

The \kepler\ mission has demonstrated that space-based transiting
planet surveys identify planet candidates at a rate much faster than
traditional follow-up techniques can confirm them.  As a result, false
positive probability quantification techniques are now an integral
part of the landscape of exoplanet science.  While the present work is
the first large-scale demonstration of a fully automated validation
procedure, there is much progress still to be made.  For example,
there is currently no support within \vespa\ to calculate the FPP for
a candidate which has a \emph{specifically identified} but hitherto
unknown close companion.  Future development plans for the
\vespa\ package include support for this scenario, as well as other
improvements.  One of the most important of these will be to allow for
a contaminating EB to not be fully contained within the target
photometric aperture; that is, modeling the probability for
further-away stars to be EBs contributing only a small amount of their
flux to the target photometry, such as is the case for many of the
false positives identified via ephemeris matching by
\citet{Coughlin:2014}.  Full inclusion of this effect will allow for
even low-SNR candidates to receive confident \vespa\ analysis, which
is now limited only to KOIs for which confident pixel-level positional
analysis is possible.

@@

\begin{turnpage}
%\capstartfalse
\input{table_fpp}
%\capstarttrue
\end{turnpage}
